Microlensing as a possible probe of event-horizon structure in quasars

### 2016-10-03 paper1/ms.tex
changes

\begin{figure}
\includegraphics[width = .49\textwidth]{figures/figure_rhalf.eps}
\caption{\label{fig:geom_crescent} Geometry of crescent sources.}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_all.eps}
    \includegraphics[width = 0.48\textwidth]{figures/4source_magnification.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurves of crescents, Gaussian and disk for sources with identical $S_0$ and $r_{1/2}$. Crescent source has $r_{1/2}$ = 0.72754 $R_p$, $R_n$ = 0.4 $R_p$, a = 0.3/-0.3 $R_p$ }
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_var_a.eps}
    \includegraphics[width = 0.48\textwidth]{figures/4avar_magnification.eps}
\caption{\label{fig:a_var} Lightcurves of crescent sources with $R_n$
  = 0.4 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_var_rn_a_poz.eps}
    \includegraphics[width = 0.48\textwidth]{figures/5Rn_back_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent_back} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_var_rn_a_neg.eps}
    \includegraphics[width = 0.48\textwidth]{figures/5Rn_forw_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve of forwards crescents with a = -0.3 $R_p$.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width = .49\textwidth]{figures/figure_rhalf.eps}
\caption{\label{fig:geom_crescent} Geometry of crescent sources: the source can be seen as a superposition of a smaller dark disk over and inside a larger brighter disk. $R_p$ and $R_n$ mark the radii of the bright and dark disk. $d_c$ and $c$ mark the distance from the center of the bright disk to the centroid and from the dark disk to the centroid.  }
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_all.eps}
    \includegraphics[width = 0.48\textwidth]{figures/4source_magnification.eps}
\caption{\label{fig:lightcurve_gauss} 1D profiles (top panel) and simulated lightcurves (bottom) of crescent, Gaussian and disk sources with identical total flux ($S_0$) and half-light radius($r_{1/2}$). Crescent source has $r_{1/2}$ = 0.72754 $R_p$, $R_n$ = 0.4 $R_p$, a = 0.3/-0.3 $R_p$. }
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_var_a.eps}
    \includegraphics[width = 0.48\textwidth]{figures/4avar_magnification.eps}
\caption{\label{fig:a_var} 1D profiles (top panel) and simulated lightcurves (bottom) of crescent sources with identical $R_p$ and $R_n$ ($R_n$ = 0.4 $R_p$) and different disk centers displacement (a).}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_var_rn_a_poz.eps}
    \includegraphics[width = 0.48\textwidth]{figures/5Rn_back_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent_back} 1D profiles (top panel) and simulated lightcurves (bottom) of backwards crescent sources with identical $R_p$ and $a$ ($a$ = 0.3 $R_p$) and different dark disk radii ($R_n$).}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/S1D_var_rn_a_neg.eps}
    \includegraphics[width = 0.48\textwidth]{figures/5Rn_forw_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent} 1D profiles (top panel) and simulated lightcurves (bottom) of forwards crescent sources with identical $R_p$ and $a$ ($a$ = - 0.3 $R_p$) and different dark disk radii ($R_n$). }
\end{figure}
